\begin{itemize}

\item{\textbf{Alquicira-Hernandez J.}, Powell J. E., Phan T. G.. \textbf{\textit{No evidence that plasmablasts transdifferentiate into developing neutrophils in severe COVID-19 disease}}. Clinical & Translational Immunology 10 (7), e1308. (2020). \\
https://doi.org/10.1002/cti2.1308}

\item{Yazar S.†, \textbf{Alquicira-Hernandez J.†}, Wing K†, Senabouth A, Gordon M. G., Andersen S, Lu Q, Rowson A, Taylor T.R.P, Clarke L, Maccora K, Chen C, Cook A.L, Ye C.J., Fairfax K.A., Hewitt A.W.*, Powell J.E.*. \textbf{\textit{Population-scale single-cell eQTL mapping identifies cell type specific genetic control of autoimmune disease}}. (2010). Under revision in \textit{Science}. \\
\textbf{† joint 1st author}}

\item{Võsa U., Claringbould A., Westra H-J., Bonder M. J., Deelen P, ..., \textbf{Alquicira-Hernandez J.}, et al, Powell J. E., Gibson G., Esko T., Franke L.. \textbf{\textit{Large-scale cis- and trans-eQTL analyses identify thousands of genetic loci and polygenic scores that regulate blood gene expression}}. (2020).
Nature Genetics in Press. \\
\url{https://doi.org/10.1101/447367}}

\item{\textbf{Alquicira-Hernandez J.}, Powell J. E. \textbf{\textit{Nebulosa recovers single-cell gene expression signals by kernel density estimation}}.
Bioinformatics, btab003. (2021). \\
https://doi.org/10.1093/bioinformatics/btab003}

\item{\textbf{Alquicira-Hernandez J.†}, Yazar S.†, Wing K, Senabouth A, Andersen S, Fairfax K.A., Hewitt A.W.†, Powell J.E.†. Single-cell gene expression reveals cell-type-specific heritability in immune cells. (2020). Under revision in Nature Genetics. \\
† joint 1st author}

\item{Wilson S. B., Howden S. E., Vanslambrouck J. M., Dorison A., \textbf{Alquicira-Hernandez J}, Powell J. E., Little M. H.. \textbf{\textit{DevKidCC allows for robust classification and direct comparisons of 4 kidney organoid datasets}}. (2020). Under revision in Genome Biology}


\item{Avila Cobos, F., \textbf{Alquicira-Hernandez, J.}, Powell, J.E. Mestdagh P., De Preter K.. \textit{\textbf{Benchmarking of cell type deconvolution pipelines for transcriptomics data}}.
Nature Communications 11, 5650. (2020). \\
\url{https://doi.org/10.1038/s41467-020-19015-1}}

\item{Chavez J., Barberena-Jonas C., Sotelo-Fonseca J. E., \textbf{Alquicira-Hernandez J.}, Salgado H, Collado-Torres L., Reyes A. \textbf{\textit{Programmatic access to bacterial regulatory networks with regutools}}, Bioinformatics, 36, 16, 15, 4532–4534 (2020), \\
\url{https://doi.org/10.1093/bioinformatics/btaa575}}

\item{\textbf{Alquicira-Hernandez J.}, Sathe A., P Ji H., Nguyen Q., Powell J. E. \textbf{\textit{scPred: accurate supervised method for cell-type classification from single-cell RNA-seq data}.}.
Genome Biology. (2019).\\
\url{https://doi.org/10.1101/369538}}

\item{Senabouth A., Lukowski S., \textbf{Alquicira-Hernandez J.}, Andersen S., Mei X., Nguyen Q., Powell J. E. (2019). \textbf{\textit{ascend: R package for analysis of single cell RNA-seq data}}.
GigaScience. \\
\url{https://doi.org/10.1093/gigascience/giz087}}

\item{Nellore A, Jaffe AE, Fortin JP, \textbf{Alquicira-Hernandez J} , Collado-Torres L, Wang S, Phillips RA, Karbhari N, Hansen KD, Langmead B, Leek JT (2016). \textbf{\textit{Human splicing diversity across the Sequence Read Archive}}.
Genome Biology.\\
\url{https://doi.org/10.1186/s13059-016-1118-6}}

\item{Nellore A., Collado-Torres L., Jaffe A. E., \textbf{Alquicira-Hernandez J.} , Pritt J., Morton J., Leek J. T., Langmead B. (2016). \textbf{\textit{Rail-RNA: Scalable analysis of RNA-seq splicing and coverage}}.
Bioinformatics  \\
\url{https://doi:10.1093/bioinformatics/btw575}}


\end{itemize}
